Collective excitations in competing phases in two and three dimensions

### 2024-03-26 paper/main.tex
cdw peak evolution

Furthermore, we found the exciton peak in $\spectral{CDW}$ also at large values of $V$ in the CDW phase, 
evolving smoothly from the CDW-AFM phase transition. \red{Das kannst Du vllt. noch stichprobenartig pruefen.}
We assume that this peak is always located outside of the two-particle continuum, even for small values of $V$.
In this case, however, it can lie very close to the continuum, so that we cannot resolve it due to the limited accuracy of our numerics.
So it seems to appear as a singularity at $2\Delta$ for small values of $V$.
\red{Stimmst Du dieser Darstellung zu?} \blue{Ja.}

>>>>

Furthermore, we found the exciton peak in $\spectral{CDW}$ also at large values of $V$ in the CDW phase, 
evolving smoothly from the CDW-AFM phase transition. \red{Das kannst Du vllt. noch stichprobenartig pruefen.} \blue{Tut es.}
We assume that this peak is always located outside of the two-particle continuum, even for small values of $V$.
In this case, however, it can lie very close to the continuum, so that we cannot resolve it due to the limited accuracy of our numerics.
So it seems to appear as a singularity at $2\Delta$ for small values of $V$.
\red{Stimmst Du dieser Darstellung zu?} \blue{Ja.}
